#This is an R program to apply Random Forest regression technique on housing sales prices prediction

```{r}
setwd("C:/Users/jo053424/Desktop/casas")
library(readr) # CSV file I/O, e.g. the read_csv function
library(randomForest)    # For Random Forest
library(caret)        # createDataPartition()
```

#Reading train and test data

```{r}
df_train <- read.csv("train.csv",header=T)

df_test <- read.csv("test.csv",header=T)

dim(df_train)
dim(df_test)

str(df_train)
```

#Check for NA and Applying na.roughfix to replace NAs with column medians
```{r}
df_train<-na.roughfix(df_train)
df_test<-na.roughfix(df_test)

sum(is.na(df_train))
sum(is.na(df_test))
```
#Partition training dataset into training and validation
```{r}
trainInd<-createDataPartition(df_train$SalePrice,
                                p=0.8,
                                list=FALSE)

train_housing<-df_train[trainInd,]
valid_housing<-df_train[-trainInd,]
```

#Apply Random Forest technique
```{r}
rf_model_housing <-train(SalePrice ~., # Standard formula notation
                  data=train_housing[,-1],  # Excclude 'id'
                  method="rf",              # randomForest
                  nodesize= 10,              # 10 data-points/node. Speeds modeling
                  ntree =500,               # Default 500. Reduced to speed up modeling
                  trControl=trainControl(method="repeatedcv", number=2,repeats=1),  # cross-validation strategy
                  tuneGrid = expand.grid(mtry = c(123))
  )
  
rf_model_housing
```
#Make predictions on validation dataset
```{r}
pred_results <- predict(rf_model_housing,
                       valid_housing,
                       type = "raw")

pred_df <- data.frame(pred_results)
valid_verify_df <- cbind(valid_housing$SalePrice,pred_df)
head(valid_verify_df)
```

#Make predictions on test dataset
```{r}
SalePrice <- predict(rf_model_housing,
                       df_test,
                       type = "raw")

SalePrice <- data.frame(SalePrice)

test_verify_df <- cbind("Id" = df_test$Id, SalePrice)
head(test_verify_df)
```

#Create submission csv
```{r}
write.csv(test_verify_df,file="Sahil_Yagnik_submission.csv", quote = FALSE, row.names = FALSE)
```